Real Estate

### 2022-11-13 src/real_estate.Rmd
multiplied monthly rents by 12

```{r}
# combine real estate and demographic data by cbsa
MSA_RE_ratios <- MSA_realEstate_compiled %>% 
      # calculate income to home price
  mutate(income_to_homeprice = median_income_usd_2021/house_price_2021) %>% 
  # calculate rent to income ratio
  mutate(avg_rent_to_income = avg_rent_2021/median_income_usd_2021) %>% 
  mutate(med_rent_to_income = median_rent/median_income_usd_2021)

@@

```{r}
# normalize columns into new data table
n_MSA_realEstate <- MSA_RE_ratios %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_avg_rent_to_income = (avg_rent_to_income- min(avg_rent_to_income, na.rm = TRUE)) / (max(avg_rent_to_income, na.rm = TRUE) - min(avg_rent_to_income, na.rm = TRUE))) %>% 
  mutate(n_med_rent_to_income = (med_rent_to_income- min(med_rent_to_income)) / (max(med_rent_to_income) - min(med_rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice))) %>% 
  mutate(n_avg_occupancy = (avg_occupancy_21 - min(avg_occupancy_21, na.rm = TRUE)) / (max(avg_occupancy_21, na.rm = TRUE) - min(avg_occupancy_21, na.rm = TRUE))) %>% 
  mutate(n_rent_change = (avg_rent_change - min(avg_rent_change, na.rm = TRUE)) / (max(avg_rent_change, na.rm = TRUE) - min(avg_rent_change, na.rm = TRUE)))

>>>>

```{r}
# combine real estate and demographic data by cbsa
MSA_RE_ratios <- MSA_realEstate_compiled %>% 
      # calculate income to home price
  mutate(income_to_homeprice = median_income_usd_2021/house_price_2021) %>% 
  # calculate rent to income ratio
  # multiply monthly rent x 12 for annual rent!
  mutate(avg_rent_to_income = (avg_rent_2021*12)/median_income_usd_2021) %>% 
  mutate(med_rent_to_income = (median_rent*12)/median_income_usd_2021)

@@

```{r}
# normalize columns into new data table
n_MSA_realEstate <- MSA_RE_ratios %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>% 
  # normalize employment growth
  mutate(n_employ_change = (employment_yo_y21_22 - min(employment_yo_y21_22)) / (max(employment_yo_y21_22) - min(employment_yo_y21_22))) %>% 
  # normalize rent to income
  mutate(n_avg_rent_to_income = (avg_rent_to_income- min(avg_rent_to_income, na.rm = TRUE)) / (max(avg_rent_to_income, na.rm = TRUE) - min(avg_rent_to_income, na.rm = TRUE))) %>% 
  mutate(n_med_rent_to_income = (med_rent_to_income- min(med_rent_to_income)) / (max(med_rent_to_income) - min(med_rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice))) %>% 
  # normalize occupancy data
  mutate(n_avg_occupancy = (avg_occupancy_21 - min(avg_occupancy_21, na.rm = TRUE)) / (max(avg_occupancy_21, na.rm = TRUE) - min(avg_occupancy_21, na.rm = TRUE))) %>% 
  # normalize rent change
  mutate(n_rent_change = (avg_rent_change - min(avg_rent_change, na.rm = TRUE)) / (max(avg_rent_change, na.rm = TRUE) - min(avg_rent_change, na.rm = TRUE)))
